---
title: "HW#8"
author: "Farzan Karimi-Malekabadi"
date: '2022-04-13'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-pkg, message=FALSE, warning=FALSE}
library(ggplot2)  # for plots
library(magrittr)  # for `%>%` operator
library(here)
library(readxl)  # for reading excel files
library(modelsummary)  # for summarizing data
library(rstan)
rstan_options(auto_write = TRUE)  # save compiled STAN object
options(mc.cores = 2)  # use two cores
library(posterior)
library(bayesplot)
theme_set(theme_classic() +
    theme(panel.grid.major.y = element_line(color = "grey92")))
library(psych)  
library(tidyverse)  
library(readr)
library(lmerTest)
library(brms)
```

# Research Question

> Can endorsement of six moral values predict the collective nostalgia proneness across 19 different cultures?

# Variables

- `profevaluation`: evaluation rating of the instructor: 1 (very unsatisfactory) to 5 (excellent)
- `nonenglish`: 1 = non-native English speakers, 0 = native-English speakers

## Import Data

```{r beauty, message=FALSE, warning=FALSE}
nos_source_d = read_csv("19 cultures.csv")

nos_d = nos_source_d %>% select(
                        CARE_tot,EQUALITY_tot,
                        PROPORTIONALITY_tot,
                        LOYALTY_tot,AUTHORITY_tot,
                        PURITY_tot,Nostalgia,
                        porient_1,age,religiosity_1,
                        starts_with(c("CoNos")),country
                        )%>%
                         mutate(
                        C_Nostalgia = ((CoNos1+CoNos2+CoNos3+CoNos4)/4),
                        moral_Ind = (CARE_tot+EQUALITY_tot+PROPORTIONALITY_tot)/3,
                        moral_Group = (LOYALTY_tot+AUTHORITY_tot+PURITY_tot)/3,
                        mean_Care = mean(CARE_tot),
                        mean_Equality = mean(EQUALITY_tot),
                        mean_Propotionality = mean(PROPORTIONALITY_tot),
                        mean_Loyalty = mean(LOYALTY_tot),
                        mean_Authority = mean(AUTHORITY_tot),
                        mean_Purity = mean(PURITY_tot),
                        mean_Age = mean(age,na.rm=TRUE),
                        mean_P_Nostalgia = mean(Nostalgia,na.rm=TRUE)
                        ) %>%
                        rename(
                        Care = CARE_tot,
                        Equality = EQUALITY_tot,
                        Propotionality = PROPORTIONALITY_tot,
                        Loyalty = LOYALTY_tot,
                        Authority = AUTHORITY_tot,
                        Purity = PURITY_tot,
                        P_Nostalgia = Nostalgia,
                        Religiosity = religiosity_1,
                        Conservatism = porient_1,
                        Age = age
                        )
```

## Variable Summary

```{r summ-var}
#Sample size in each country
 count(nos_d, country)

#summarizing data in each country

nos_d %>% 
  group_by(country) %>% 
  summarise(mean = mean(C_Nostalgia, na.rm = T), 
            SD = sd(C_Nostalgia, na.rm = T),
            Min = min(C_Nostalgia, na.rm = T),
             Max = max(C_Nostalgia, na.rm = T),
           )%>%  
  mutate_if(is.numeric, ~round(., 2)) %>% 
  print(n = 50)

# look at distribution by country
nos_d %>% 
  ggplot(aes(C_Nostalgia)) + 
  geom_density() +
  facet_wrap(~country)
```

# Model

Let $Y$ = profevaluation, $G$ = nonenglish

Model:
$$
\begin{align}
\text{Individual level:}  \\
  \texttt{C_Nostalgia}_{ij} & \sim \mathcal{N}(\mu_{ij}, \sigma)  \\
  \mu_{ij} & =\\ \beta_{0j} + \\
  \beta_{1j} \texttt{Care}_{ij} +\\
  \beta_{2j} \texttt{Equality}_{ij}+\\
  \beta_{3j} \texttt{Propotionality}_{ij}+\\
  \beta_{4j} \texttt{Loyalty}_{ij}+\\
  \beta_{5j} \texttt{Authority}_{ij}+\\
  \beta_{6j} \texttt{Purity}_{ij}+\\
  \beta_{7j} \texttt{P_Nostalgia}_{ij}+\\
  \beta_{8j} \texttt{Religiosity}_{ij}+\\
  \beta_{9j} \texttt{Conservatism}_{ij}+\\
  \beta_{10j} \texttt{Age}_{ij}\\
  
 \text{County level:}  \\ 
\beta_{0j} & \sim \mathcal{N}(\mu^{[\beta_0]}, \tau^{[\beta_0]})  \\

\end{align}
$$

Prior:


## Running brms

We used 4 chains, each with 4,000 iterations (first 2,000 as warm-ups). 

```{r m1, eval=FALSE, include=FALSE}
m1_fit <- brm(C_Nostalgia ~ 1 + Care+ Equality+ Propotionality
                              + Loyalty+ Authority+ Purity+
                              + Conservatism + P_Nostalgia + Age 
                              + mean_Care + mean_Equality 
                              + mean_Propotionality + mean_Loyalty
                              + mean_Authority + mean_Purity
                              + mean_P_Nostalgia + mean_Age
                              + (1|country)
                              ,
                
    family = gaussian(link = "identity"),
    data = nos_d, 
    chains = 4,
    #adapt_delta = 0.99,
    iter = 4000,
    warmup = 2000,
    save_pars = save_pars(all = TRUE)
  )
```

```{r message=FALSE, warning=FALSE}
m1_fit=readRDS(file = "my_data.rds")
summary(m1_fit)
```


Get priors:

```{r}
get_prior(C_Nostalgia ~ 1 + Care+ Equality+ Propotionality
                              + Loyalty+ Authority+ Purity+
                              + Conservatism + P_Nostalgia + Age 
                              + mean_Care + mean_Equality 
                              + mean_Propotionality + mean_Loyalty
                              + mean_Authority + mean_Purity
                              + mean_P_Nostalgia + mean_Age
                              + (1|country)
                              ,
                
    family = gaussian(link = "identity"),
    data = nos_d)
```

Convergence check of MCMC
```{r}

mcmc_plot(m1_fit, type = "trace")
```
# Results

Table of coefficients

```{r summ-m1}
m1_fit %>%
    # Convert to `draws` object to work with the `posterior` package
    as_draws() %>%
    # Get summary
    summarize_draws() %>%
    # Use `knitr::kable()` for tabulation
    knitr::kable(digits = 2)
```

# Interpretations

We found evidence that loyalty, authority and purity can significantly predict collective nostalgia across 19 countries after controlling for age, personal nostalgia and age. 


